---
title: "Weather data scrape"
author: "David Heagy"
date: "9/17/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(rvest)

v <- c("Year", 
               "Day of Year", 
               "Station Number",
               "Air Temp - Max", #Celsius
               "Air Temp - Min",
               "Air Temp - Mean",
               "RH - Max", # %
               "RH - Min",
               "RH - Mean",
               "VPD - Mean",
               "Solar Rad. - Total",
               "Precipitation - Total",
               "4\" Soil Temp - Max  ( = 2\" prior to 1999 )",
               "4\" Soil Temp - Min  ( = 2\" prior to 1999 )",
               "4\" Soil Temp - Mean  ( = 2\" prior to 1999 )",
               "20\" Soil Temp - Max  ( = 4\" prior to 1999 )",
               "20\" Soil Temp - Min  ( = 4\" prior to 1999 )",
               "20\" Soil Temp - Mean  ( = 4\" prior to 1999 )",
               "Wind Speed - Mean",
               "Wind Vector Magnitude for Day",
               "Wind Vector Direction for Day",
               "Wind Direction Standard Deviation for Day",
               "Max Wind Speed",
               "Heat Units (30/12.8 C) (86/55 F)",
               "Reference Evapotranspiration (ETo) = Original AZMET",
               "Reference Evapotranspiration (ETos) = Penman-Monteith",
               "Actual Vapor Pressure - Daily Mean",
               "Dewpoint, Daily Mean")
```
Source of files: https://cals.arizona.edu/azmet/38.htm
For more information on legends and abbreviations (daily files): https://cals.arizona.edu/azmet/raw2003.htm

Also, Elevation: 840 meters (2756 ft)

USDA soil survey (2008): 
https://soilseries.sc.egov.usda.gov/OSD_Docs/S/SAHUARITA.html

USDA Soil survey (p 83, #72): https://www.nrcs.usda.gov/Internet/FSE_MANUSCRIPTS/arizona/AZ669/0/pima.pdf

USDA Soil survey (p 187) : https://www.nrcs.usda.gov/Internet/FSE_MANUSCRIPTS/arizona/AZ703/0/tohono.pdf

```{r}
url <- paste("https://cals.arizona.edu/azmet/data/38",13:19,"rd.txt", sep= "")
# raw daily weather datasets for Sahaurita from 2013-2019
df13 <- read.csv(url[1])
df14 <- read.csv(url[2])
df15 <- read.csv(url[3])
df16 <- read.csv(url[4])
df17 <- read.csv(url[5])
df18 <- read.csv(url[6])
df19 <- read.csv(url[7])
# renames columns of individual data set 
names(df13) <- v
names(df14) <- v
names(df15) <- v
names(df16) <- v
names(df17) <- v
names(df18) <- v
names(df19) <- v
# now can call on each or whole VVVV
df_13_to_19 <- rbind(df13, df14, df15,df16, df17, df18, df19)

```



```{r}
x <- df19$"Air Temp - Max"
y <- df19$"Air Temp - Min"
z <- df19$"Air Temp - Mean"
mean(x)
mean(y)
mean(z)
C_F <- function(C) {
  return ((C *9/5) + 32)
}
C_F(29.72)
```

```{r}
p13 <- df13$"Precipitation - Total"
p14 <- df14$"Precipitation - Total"
p15 <- df15$"Precipitation - Total"
p16 <- df16$"Precipitation - Total"
p17 <- df17$"Precipitation - Total"
p18 <- df18$"Precipitation - Total" # in inches
p19 <- df19$"Precipitation - Total"

sum(p13)
sum(p14)
sum(p15)
sum(p16)
sum(p17)
sum(p18)
sum(p19)
yearly_rain <- c(sum(p13), sum(p14), sum(p15), sum(p16), sum(p17), sum(p18), sum(p19))
names(yearly_rain) <- c("2013", "2014", "2015", "2016", "2017", "2018", "2019")
barplot(yearly_rain, ylab = "Collective Inches in rain over year")

s <- sd(yearly_rain)
m <- mean(yearly_rain)
m+(2*s)
m-(2*s)
summary(yearly_rain)
```
Rainfall is below expectation.  

Since the Orly parameters of rain is 800m^3 (assuming we just need to take cubic root, area and height equal), which is appx equal to 9.28m = 365 inches

I just summed all the rain over the year for each year in Sahaurita, and then averaged the collective sums and took standard deviations. 
1sd

153.5212, 329.9017

2sd

65.33092, 418.0919


Also, since median is less than mean, it is left-skewed.

```{r}
names(df19)
```





For outputting csv file to use in tableau:
```{r}
write.csv(df_13_to_19, "Arizona_ultimate.csv")
```
  
Experimenting with rvest  
```{r}
result <- read_html("https://streamflow.watershedconnection.com/Dwr")
```
  
```{r}
s <- html_nodes(result, ".values")
s

```
```{r}
df2
```
  
  